Monte Carlo and bootstrap for ALL parameters with tables

### 2024-08-14 All_tables.Rmd
A long way to go to have pretty tables

---
title: "Monte Carlo and bootstrap for ALL parameters"
output: pdf_document
date: "2024-08-02"
---

@@

```{r}
library(readxl) # to read the initial file
library(magrittr) # for pipes
library(tibble) # for add_column
```

@@

res1 <- MonteCarlo(n, 10000)
# Just one circle to begin with

@@

res2 <- MC_boot(n, B1 = 1000, B2 = 400)
# Just one circle to begin with

@@

>>>>

---
title: "Monte Carlo and bootstrap for ALL parameters with tables"
output: pdf_document
date: "2024-08-02"
---

@@

```{r}
library(readxl) # to read the initial file
library(magrittr) # for pipes
library(tibble) # for add_column
library(xtable) # To have LaTeX tables based on dataframes
```

@@

# res1 <- MonteCarlo(n, 500)
# Just one circle to begin with

@@

res2 <- MC_boot(n, B1 = 100, B2 = 50)
# Just one circle to begin with

@@

```{r}
# Tables
print(xtable(TC_normal, caption = "Test"))
```

```{r}
# Tables
addtorow <- list()
# addtorow$pos <- list()
addtorow$pos <- c(0, 2)
# addtorow$pos[[2]] <- 4
addtorow$command <- c('\vspace{2mm} \n', '\vspace{10mm} \n')
print(xtable(TC_normal, caption = "Test", align = c("c", "|", "c", "c", "c", "c")), add.to.row = addtorow)
```
